\TITLE

### 2024-08-21 paper/main.tex
update bibliography

The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonser}.

@@

Blockchain-based dispute resolution platforms such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, nappertDecentralizedJusticeReinventing2020, gudkovCrowdArbitrationBlockchain2020}, Themis~\cite{mengThemisDecentralizedEscrow2019}, Aragon Court~\cite{AragonWhitepaper2023,aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019, lingwallShouldCodeBe2019} offer a promising direction. These systems could employ a pool of field experts who, in the event of a dispute, would examine the smart contract, the proofs ( $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) and provide verdicts. Expert participation and honest verdicts are encouraged through a system of fees, stakes and rewards. At the time of writing Kleros is the most successful platform for resolving consumer disputes in e-commerce or collaborative economy. It has received funding from the Commission's European Innovation Council~\cite{CommissionEuropeanInnovation2020}. The protocol claims to have resolved 1645 disputes, employing 716 jurors and rewarding them with 401 ETH~\cite{KlerosHomepage}. Kleros allows integration with new protocols and we leave it to future work.

@@

\begin{sloppypar}
For instance, we could employ the Ethereum network and utilize privacy mixers to ensure private payments. Nevertheless, privacy mixers have drawn scrutiny from regulators because they are increasingly used by malicious actors to obscure the origins of funds illicitly. A notable example is Tornado Cash, the largest privacy mixer to date, which has faced sanctions across significant portions of the Ethereum network. Ongoing research into compliant privacy mixers, such as the Voluntary Reveal Approach proposed in~\cite{dotanHazeCompliantPrivacy2023}, seeks to address these concerns. This approach involves Proofs of Innocence required before a user can access the system and incorporates oracles for monitoring sanctioned addresses—currently maintained on the Ethereum blockchain by Chainalysis~\cite{ChainalysisOracleSanctions}.
\end{sloppypar}

@@

\begin{sloppypar}
Through rigorous definition and analysis, we have demonstrated that our protocol meets the criteria for fairness, as outlined in Definition~\ref{def:fairness}. It does so by systematically publishing proofs of delivery, payment, and provisioning, ensuring a transparent and equitable process for all parties involved.
\end{sloppypar}

@@

\paragraph{Data availability}
No data was used for the research described in the article.
The prototype is available at \url{https://anonser.stan.bar}. 
The source code is available at \url{https://github.com/stanbar/anonser}.

>>>>

The source code is available at \url{https://github.com/stanbar/anonser}.

@@

Blockchain-based dispute resolution platforms such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, nappertDecentralizedJusticeReinventing2020, gudkovCrowdArbitrationBlockchain2020}, Themis~\cite{mengThemisDecentralizedEscrow2019}, Aragon Court~\cite{AragonWhitepaper2023,aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019, lingwallShouldCodeBe2019} offer a promising direction. These systems could employ a pool of field experts who, in the event of a dispute, would examine the smart contract, the proofs ( $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) and provide verdicts. Expert participation and honest verdicts are encouraged through a system of fees, stakes and rewards. At the time of writing Kleros is the most successful platform for resolving consumer disputes in e-commerce or collaborative economy. It has received funding from the Commission's European Innovation Council~\cite{europeancommissionCommissionEuropeanInnovation2020}. The protocol claims to have resolved 1645 disputes, employing 716 jurors and rewarding them with 401 ETH~\cite{KlerosHomepage}. Kleros allows integration with new protocols and we leave it to future work.

@@

\begin{sloppypar}
For instance, we could employ the Ethereum network and utilize privacy mixers to ensure private payments. Nevertheless, privacy mixers have drawn scrutiny from regulators because they are increasingly used by malicious actors to obscure the origins of funds illicitly. A notable example is Tornado Cash, the largest privacy mixer to date, which has faced sanctions across significant portions of the Ethereum network. Ongoing research into compliant privacy mixers, such as the Voluntary Reveal Approach proposed in~\cite{dotanHazeCompliantPrivacy2023}, seeks to address these concerns. This approach involves Proofs of Innocence required before a user can access the system and incorporates oracles for monitoring sanctioned addresses—currently maintained on the Ethereum blockchain by Chainalysis~\cite{chainalysisChainalysisOracleSanctions}.
\end{sloppypar}

@@

\begin{sloppypar}
Through rigorous definition and analysis, we have demonstrated that our protocol meets the criteria for fair-exchange protocol, as shown in in Section~\ref{sec:fairness-analysis}. It does so by systematically publishing proofs of delivery, payment, and provisioning, ensuring a transparent and equitable process for all parties involved.
\end{sloppypar}

@@

\paragraph{Data availability}
No data was used for the research described in the article.
The source code is available at \url{https://github.com/stanbar/anonser}.
